hormones

### 2019-11-13 analysis/07_hormones.Rmd
now with axis text

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
    droplevels() %>% 
  ggplot(aes(x = as.numeric(treatment), y = plasma_conc)) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(outlier.colour = treatment, fill = treatment, alpha = sex)) +
    mytheme() +
    theme(axis.text.x =  element_blank(),
          legend.position = "none") +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) +
    guides(fill = guide_legend(order=1),
         color = guide_legend(order=2)) +
    scale_alpha_manual(values = c(0.75,1)) +
    scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) 
  }

@@

```{r sexsteroids}
b <- hormonecharplot("cort", "CORT (ng/mL)")
c <- hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
d <- plot_grid(d1,d2, nrow = 1)
bcd <- plot_grid(b ,c, d, ncol = 1)
bcd
```

>>>>

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
    droplevels() %>% 
  ggplot(aes(x = as.numeric(treatment), y = plasma_conc)) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(outlier.colour = treatment, fill = treatment, alpha = sex)) +
    mytheme() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
          legend.position = "none") +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) +
    guides(fill = guide_legend(order=1),
         color = guide_legend(order=2)) +
    scale_alpha_manual(values = c(0.75,1)) +
    scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                       labels = c( "control", "bldg", "lay", "inc.d3", 
                                   "inc.d9", "inc.d17", "hatch", "n5", "n9"))
  }

@@

```{r sexsteroids}
hormonecharplot("cort", "CORT (ng/mL)")
hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
plot_grid(d1,d2, nrow = 1)
